---
title: "Birthday Problem"
author: "Zachary Lilley"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Birthday Problem}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Mathematical Derivation
Individual Probabilities:

- Person 1: Can have any birthday $p = \frac{365}{365}$

- Person 2: Can have a different birthday $p = \frac{364}{365}$

- Person 3: Must differ from 1 and 2 $p = \frac{363}{365}$

- Person n: Must differ from all previous $(n-1)$ people $p = \frac{365 - n + 1}{365}$

Supplements:
$$
A = \text{2 or more shared birthdays} \newline
\bar A = \text{no shared birthdays}
$$

So the probability they are all different:
$$
P(\bar A) = P(all~different) = \frac{365!}{(365 - n)!\times365^n}
$$
This implies that:
$$
P(\bar A) = \frac{365!/(365-n)!}{365^n} = \frac{{}^{365}P_{n}}{365^n} \newline AND \newline
P(A) = 1 - P(\bar A)
$$

Now we can use the Division Rule of Logs to say:
$$
log(P(\bar A)) = log({}^{365}P_{n}) - n~log(365) 
$$

And so with Stirling Approximation where $log(n!) \approx n~log~n - n$:
$$
log({}^{365}P_{n}) = log(365!) + log{365\choose{n}} - n~log(365)
$$
Simplifying:
$$
P(\bar A) = log(n!) +log{365\choose{n}} - n~log(365)
$$
Recall: $P(A) = 1 - P(\bar A)$
And adding a little R, and reversing the logs, we can write the function as:
$$
P(A) \approx 1 - exp(P(\bar A)) = \newline
1 - exp(log(choose(365,n)) + log(factorial(n)) - n~log(365))
$$

```{r setup}
library(MATH4753F25lilley)
```

# Function body for Birthday Prediction
```{}
1-exp(lchoose(365,x) + lfactorial(x) - x*log(365))
```

# Implementing the Birthday function to find probability of 2 or more people in a class of n people that share a birthday
```{r}
MATH4753F25lilley::birthday(20:24)
```





