---
title: "Demonstrating Four Key Functions"
author: "Zachary Lilley"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Demonstrating Four Key Functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 5
)
library(MATH4753F25lilley)
```

## 1. Normal Curve with Shaded Area

The `myncurve()` function plots a normal distribution and shades the area up to a specified value:
```{r}
myncurve(mu = 10, sigma = 3, a = 12)
```

## 2. Bootstrap Confidence Intervals

The `myboot2()` function calculates bootstrap confidence intervals:
```{r}
set.seed(123)
sample_data <- rnorm(30, mean = 50, sd = 10)
myboot2(x = sample_data, iter = 1000, fun = "mean", alpha = 0.05)
```

## 3. Optimal Ticket Sales

The `ntickets()` function determines optimal overbooking:
```{r}
ntickets(N = 200, gamma = 0.02, p = 0.95)
```

## 4. Scatter Plot with Histograms

The `scatterhist()` function creates a scatter plot with marginal histograms:
```{r}
x <- rnorm(50, mean = 5, sd = 2)
y <- 2*x + rnorm(50, mean = 0, sd = 1)
scatterhist(x, y, xlab = "X values", ylab = "Y values")
```
